### 2025-08-30 sections/5-discussion.tex
minor revisions

HNSW and ANNOY maintain near-constant throughput as the cardinality grows, but their recalls decline and their index build time and memory rise, making them unsuitable when datasets grow exponentially.
CAKES's tree builds orders of magnitude faster with far less memory; while queries are slower than HNSW/ANNOY, CAKES attains near-constant scaling with perfect recall.

>>>>

HNSW and ANNOY maintain near-constant throughput as the cardinality grows, but their recalls decline and their index build times rise, making them unsuitable when datasets grow exponentially.
CAKES's tree builds orders of magnitude faster; while queries are slower than HNSW/ANNOY, CAKES attains near-constant scaling with perfect recall.
